Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-19 paper/main.tex
some corrections of discussions 2nd half

%#6
% hypothesis
Based on the report by \cite{aziz2008modulation}, we hypothesized that semantic spatial
information embedded in the audio-description would correlate with
increased hemodynamic activity in the PPA. However, methods and results presented
here differ from this previous study in key aspects.
% diff to Aziz (2008)
\cite{aziz2008modulation} modeled events from onset to offset of sentences,
describing unknown and famous places and faces, and compared activity levels
that were averaged across voxels of ROIs (PPA and fusiform face area, FFA
\citep{kanwisher1997ffa}) defined by a localizer experiment.
% Aziz results
Their results showed decreased activity in only the left PPA
compared to activity in the FFA for sentences describing famous places in contrast
to famous faces.
% we: model & whole brain
Here, we modeled events from onset to offset of single words and performed a
voxelwise whole-brain analysis.
% our results
Group results of the audio-description's primary contrast yielded significantly
increased hemodynamic activity spatially restricted to the anterior part of the
PPA group overlap.
% concluding statement
Contrary to \cite{aziz2008modulation}, our results suggest that auditory
spatial information compared to non-spatial information correlates with
bilaterally increased activation in the anterior part of the PPA.

%#7
% previous studies: no task
It is common for conventional localizer paradigms to
employ a task to keep participants attentive to the stimuli.
% but: Epstein (1998)
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a perceptual judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
The naturalistic stimulation paradigm employed here is similar in the sense that participants had no behavioral or
cognitive task \cite[e.g., forming a mental image of the stimuli;][]{ocraven2000mental} but just had to ``enjoy the presentation''.
% but still: we are different
This naturalistic paradigm nevertheless differs from \cite{epstein1998ppa},
because the relevant stimulus features were embedded in a continuous stream of complex
auditory (and visual) information which makes it unlikely that participants
speculated on the purpose of the investigation or perform undesired and unknown
evaluation or categorization of isolated stimuli.
% concluding statement: kinda automatic process
Our results therefore indicate that verbally communicated spatial information
is processed, in the anterior PPA, automatically and without specifically
guided attention.

% shortcomings
%#2
Our approach to stimulus annotation and event selection
differs from previous reports in the literature.
% PPA: intro
In an earlier study, \cite{bartels2004mapping} manually annotated the content of
individual movie frames (color, faces, language, and human bodies) and found
that the functional specialization of brain areas is preserved during movie
watching.
%
In contrast, we aimed to exploit a cinematographic confound in the structure of
movies, where
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the spatial layout of locations in earlier
shots and later focus more on detailed depictions of people and objects
\citep{brown2012cinematography, katz1991film, mascelli1998five}.
%#8
% optimal stimulus type in vision
Moreover, in the visual domain, pictures of landscapes and not pictures of landmarks or
buildings are considered to be the ``optimal'' stimulus type
\citep{epstein2008parahippocampal}.
% we did not choose se\_new and se\_old
In the audio-description's primary contrast, we did not include the categories
that contain switches from one setting to another (\texttt{se\_new} and
\texttt{se\_old}) which one might assume to contain the auditory equivalent to
pictures of landscapes.
% why
The reason was that the categories \texttt{se\_new} and \texttt{se\_old} were
heterogeneous: they rarely contained holistic (but also vague) descriptions of
landscapes (e.g.  ``[Forrest is running through the] jungle'') but mostly
landmarks or buildings, and also non-spatial hints (e.g. ``[Jenny as a]
teenager``).
% visual system => gist in milliseconds
Humans can identify the gist of a rich visual scene within the duration of a
single fixation \citep{henderson2003human}.
%
Hence, further studies might investigate if vague verbal descriptions of
landscapes lead to a different hemodynamic activity level than descriptions of
more concrete parts of a scene (e.g.``[a] beacon'', [a] ``farmhouse'').
%#5
% results
Lastly, the group results of the movie stimulus' primary contrast yielded a large cluster
that spans the group overlap of individual PPA ROIs from anterior to posterior.
% confound of higher perception
The cluster's extent into more posterior, earlier visual areas could be
an indication that the temporal averaging across events suffered from
insufficient controlling for confounding visual features.
% solution
Future studies that aim to use a movie to localize visual areas in individual
participants should extensively annotate the content of frames \citep[e.g.,
using the open-source solution ``Pliers'' for feature extraction from a visual
naturalistic stimulus;][]{mcnamara2017developing}.

@@

%#12
% RSC + LOC
Apart from the PPA, results show significantly increased activity in the
dorsal precuneus and posterior cingulate region (e.g. retrosplenial complex;
RSC) and lateral occipital cortex (LOC; more lateral in the movie stimulus, more
medial in the audio-description stimulus) for both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly exhibited increased hemodynamic activity
in studies investigating visual spatial perception or navigation (see
\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
% not random shit
Thus, our model-driven approach to operationalize spatial perception based on stimulus
annotations reveals focussed activation patterns in networks that are implicated
in visual spatial perception and cognition.

%#13 natural stimulation
In summary, natural stimuli like movies \citep{eickhoff2020towards,
hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
silbert2014coupled, wilson2008beyond} can be used as a continuous, complex,
immersive, task-free paradigm that more closely resembles our natural dynamic
environment than traditional experimental paradigms.
% method
We took advantage of three fMRI datasets and two stimulus annotations that are
part of the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org} to operationalize the
perception of spatial information embedded an audio-visual movie and an
auditory narrative, and compare current results to a previous report of a
conventional, block-design localizer.
% results
This report offers evidence that a model-driven GLM analysis based on
annotations can be applied to naturalistic paradigm to localize concise
functional areas and networks correlating with specific perceptual processes.
% interpretation
More specifically, our results demonstrate that increased activation in the PPA
during the perception of static pictures generalizes to the perception of
spatial information embedded in a movie and an exclusively auditory stimulus.
% interpretation: aPPA vs. pPPA
Further, our results provide evidence that the PPA can be divided into
functional subregions that coactivate during the perception of visual scenes.
% interpretation
Finally, the presented evidence on the in-principle suitability of a naturally
engaging, purely auditory paradigm for localizing the PPA may offer a path to
the development of diagnostic procedures more suitable for individuals with
visual impairments or conditions like nystagmus.

>>>>

%#6 hypothesis
Based on the report by \cite{aziz2008modulation}, we hypothesized that semantic
spatial information embedded in the audio-description would correlate with
increased hemodynamic activity in the PPA.
%
Methods and results presented here differ from this previous study in key
aspects.
% diff to Aziz (2008)
\cite{aziz2008modulation} modeled events from onset to offset of sentences,
describing unknown and famous places and faces, and compared activity levels
that were averaged across voxels of ROIs (PPA and fusiform face area, FFA
\citep{kanwisher1997ffa}) defined by a localizer experiment.
% Aziz results
Their results showed decreased activity in only the left PPA
compared to activity in the FFA for sentences describing famous places in contrast
to famous faces.
% we: model & whole brain
Here, we modeled events from onset to offset of single words and performed a
voxelwise whole-brain analysis.
% our results
Group results of the audio-description's primary contrast yielded significantly
increased hemodynamic activity spatially restricted to the anterior part of the
PPA group overlap.
% concluding statement
Contrary to \cite{aziz2008modulation}, our results suggest that auditory
spatial information compared to non-spatial information correlates with
bilaterally increased activation in the anterior part of the PPA.

%#7
% previous studies: no task
It is common for conventional localizer paradigms to
employ a task to keep participants attentive to the stimuli.
% but: Epstein (1998)
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a perceptual judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
The naturalistic stimulation paradigm employed here is similar in the sense that participants had no behavioral or
cognitive task \cite[e.g., forming a mental image of the stimuli;][]{ocraven2000mental} but just had to ``enjoy the presentation''.
% but still: we are different
Nevertheless, the naturalistic paradigm differs from \cite{epstein1998ppa},
because the relevant stimulus features were embedded in a continuous stream of complex
auditory (and visual) information which makes it unlikely that participants
speculated on the purpose of the investigation, or performed undesired and unknown evaluation or categorization of isolated stimuli.
% concluding statement: kinda automatic process
Our results therefore indicate that verbally communicated spatial information
is processed, in the anterior PPA, automatically and without specifically
guided attention.

% shortcomings
%#2
Our approach to stimulus annotation and event selection
differs from previous reports in the literature.
% PPA: intro
In an earlier study, \cite{bartels2004mapping} manually annotated the content of
individual movie frames (color, faces, language, and human bodies) and found
that the functional specialization of brain areas is preserved during movie
watching.
%
In contrast, we aimed to exploit a cinematographic confound in the structure of
movies, where
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the spatial layout of locations in earlier
shots and later focus more on detailed depictions of people and objects
\citep{brown2012cinematography, katz1991film, mascelli1998five}.
% results
The group results of the movie stimulus' primary contrast yielded a large cluster
that spans the group overlap of individual PPA ROIs from anterior to posterior.
% confound of higher perception
The cluster's extent into more posterior, earlier visual areas could be
an indication that the temporal averaging across events suffered from
insufficient controlling for confounding visual features.
% solution
Future studies that aim to use a movie to localize visual areas in individual
participants should extensively annotate the content of frames \citep[e.g.,
using the open-source solution ``Pliers'' for feature extraction from a visual
naturalistic stimulus;][]{mcnamara2017developing}.

%#8
% optimal stimulus type in vision
In the visual domain, pictures of landscapes and not pictures of landmarks or
buildings are considered to be the ``optimal'' stimulus type
\citep{epstein2008parahippocampal}.
% we did not choose se\_new and se\_old
In the audio-description's primary contrast, we did not include the categories
that contain switches from one setting to another (\texttt{se\_new} and
\texttt{se\_old}) which one might assume to contain the auditory equivalent to
pictures of landscapes.
% why
The reason was that the categories \texttt{se\_new} and \texttt{se\_old} were
heterogeneous: they rarely contained holistic (but also vague) descriptions of
landscapes (e.g.  ``[Forrest is running through the] jungle'') but mostly
landmarks or buildings, and also non-spatial hints (e.g. ``[Jenny as a]
teenager``).
% visual system => gist in milliseconds
Humans can identify the gist of a rich visual scene within the duration of a
single fixation \citep{henderson2003human}.
%
Hence, further studies might investigate if vague verbal descriptions of
landscapes lead to a different hemodynamic activity level than descriptions of
more concrete parts of a scene (e.g.``[a] beacon'', [a] ``farmhouse'').
%#5

@@

%#12
% RSC + LOC
Apart from the PPA, results show significantly increased activity in the
dorsal precuneus and posterior cingulate region (e.g. retrosplenial complex;
RSC) and lateral occipital cortex (LOC; more lateral in the movie stimulus, more
medial in the audio-description stimulus) for both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly exhibited increased hemodynamic activity
in studies investigating visual spatial perception or navigation (see

% not random shit
Thus, our model-driven approach to operationalize spatial perception based on stimulus
annotations reveals focussed activation patterns in networks that are implicated
in visual spatial perception and cognition.

%#13 natural stimulation
In summary, natural stimuli like movies \citep{eickhoff2020towards,
hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
silbert2014coupled, wilson2008beyond} can be used as a continuous, complex,
immersive, task-free paradigm that more closely resembles our natural dynamic
environment than traditional experimental paradigms.
% method
We took advantage of three fMRI datasets and two stimulus annotations that are
part of the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org} to operationalize the
perception of spatial information embedded an audio-visual movie and an
auditory narrative, and compare current results to a previous report of a
conventional, block-design localizer.
% results
The current study offers evidence that a model-driven GLM analysis based on
annotations can be applied to naturalistic paradigm to localize concise
functional areas and networks correlating with specific perceptual processes.
% interpretation
More specifically, our results demonstrate that increased activation in the PPA
during the perception of static pictures generalizes to the perception of
spatial information embedded in a movie and an exclusively auditory stimulus.
% interpretation: aPPA vs. pPPA
Further, our results provide further evidence that the PPA can be divided into
functional subregions that coactivate during the perception of visual scenes.
% interpretation
Finally, the presented evidence on the in-principle suitability of a naturally
engaging, purely auditory paradigm for localizing the PPA may offer a path to
the development of diagnostic procedures more suitable for individuals with
visual impairments or conditions like nystagmus.
